Refinements for open automata

### 2022-03-07 2021-Refinement/paper/refinementarticle.tex
proof of thm

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

@@

Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in vars(s_3)}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in J'_1$:\\
The proof is based on the following facts.
First, because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
Second, we have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]\\
Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$

And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
\end{align*}
Finally, the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
Furthermore, as $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

From all the implications induced by the extension of the valuation context mentioned above, and by entering   all previous intermediate results in the formula $(*)$, we get:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
\implies  \hspace{12em}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\\
			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in \fvars{s_3}} v^1_3=v^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}   
\end{multline*}	
\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}

We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_{3}}
}\!\!\! v^1_3=v^2_3  \wedge s^{1\prime}_3 = s^{2\prime}_3 
 \end{multline*}	
Therefore, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in \fvars{s_3}} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_{3}}
}\!\!\! v^1_3=v^2_3  \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}
And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge \\
			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_3}}  v^1_3=v^2_3\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}	
Because of the domain of the substitutions of the relations, we get expected formula:\TODO{Point a verifier les substitutions!}
	\begin{multline*}
  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{multline*}

>>>>

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}
\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

@@

Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in J'_1$:\\
The proof is based on the following facts.
First, because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
Second, we have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]\\
Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$

And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
\end{align*}
Finally, the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
Furthermore, as $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

From all the implications induced by the extension of the valuation context mentioned above, and by entering   all previous intermediate results in the formula $(*)$, we get:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
\implies  \hspace{12em}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\\
			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}   
\end{multline*}	
\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}

We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
 \end{multline*}	
Therefore, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\\
			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
\land \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}
And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}	
Because of the domain of the substitutions of the relations, we get expected formula:\TODO{Point a verifier les substitutions!}
	\begin{multline*}
  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{multline*}
